Classless Java

### 2015-11-04 paper/sections/RelatedWork.tex
related work on MyType

\paragraph{ThisType/MyType/Extensibility}
\emph{This} is a polymorphic type variable.  Typical Type Systems
forClass-Based Object-Oriented PLs. Class names as types.  Inheritance as
subtyping Resulting in difficulty in reusing classes with recursive interfaces
by inheritance Standard (non)solution: downcasts Self types (often called MyType
[Bruce et al.])  OCaml

Does our approach support binary methods?

We are using covariant-return types to simulate some uses 
of ThisType/MyType. Only works on positive positions, whereas 
MyType is more general, as it works on any positions. Nevertheless 
our approach is still useful (for example for fluent interfaces).

- expression problem

@@

- SugarJ

>>>>

\paragraph{ThisType/MyType/Extensibility}
Typical object-oriented programming languages (e.g. Java) use class names as
types and inheritance as subtyping relations. This gives difficulty when
extending classes/interfaces with recursive types. Problems such as binary
methods, return type refinement, etc. emerge and hinders software extensibility
greatly.

\emph{MyType}~\cite{bruce1994paradigmatic} was proposed by Bruce and Foster,
which represents the type of \textbf{this} and changes its meaning along with
inheritance. The addition of MyType to a language will allow easy definition of
binary methods, methods with recursive types (i.e., the same type of the
receiver appears in the argument or return positions of methods), etc. MyType
greatly enhances the expressiveness and extensibility of object-oriented
programming languages.

In our approach, we are using covariant-return types to simulate some uses of
MyType. But our approach only works on method positive positions, whereas MyType
is more general, as it works on any positions. Nevertheless our approach is
still useful for modeling fluent interfaces and solving expression
problems,etc.

@@

- SugarJ~\cite{erdweg11sugarj}
